Demystifying the Computer Science PhD Admission in the US\\{\large A Guide for International Students

### 2023-11-27 demystify.tex
Updates from Overleaf

>>>>

\section{Preparing Materials}
\subsection{Sharing spreadsheets}
Many students use a spreadsheet to help them and their letter writers to keep track of their applications. You can create a personal and a shared spreadsheet but a simplest one is just a shared one (e.g., using Google sheet).  Here are some information to put on the sheet.  
\begin{itemize}
\item \textbf{Your info}: Full name, email, phone, link to website/CV).  This is helpful for the writers just in case they want to quickly get some information about you.
\item \textbf{Applications details}: University, Dept, Application System URL, Submission Deadlines, Application Status (e.g., submitted,  rejected, wait-listed, accepted)
\item \textbf{LoRs}: Writer 1, Writer 2, Writer 3.  If this is a shared document, you might want to omit names and just use writer X. Under each is their status, e.g., sent/not yet/reminder needed, etc.
\end{itemize}
